An efficient composition of bidirectional programs by tupling and lazy updates

### 2019-12-02 paper/7.conclusion.tex
small fixes

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative BX composition programs, we know that $put_m$ is fastest method if input size is not large and $xpg$ is fastest for other left associative programs.
This shows that if programmer choose one method based on the their BX programs and inputs, they can use efficient evaluation.

@@

We will continue our work on the following three points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs and restriction for $\pginline{Case}$ in Section~\ref{sect:pg}. To be a practical evlauation method, extention of the target language is needed. After extention of the language, we can evaluate more various programs for experimental results.

@@

Third is introducing type systems to datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages. We need to investigate more about $construct\_dummy$, because current definition that is used in Section~\ref{sect:experiments} will cause type errors.

>>>>

In this paper, we focus on efficiency of composition of BX programs.
To achieve fast evaluation, we introduce two different methods using memoization.
From the experimental results of left associative BX composition programs, we know that $put_m$ is fastest method if input size is not large and $xpg$ is fastest for other left associative programs.
This shows that if programmers choose one method based on the their BX programs and inputs, they can use an efficient evaluation method.

@@

We will continue our work on the following three points.
First is overcomming our limitation in $xpg$. In $xpg$, there are two limitations: only for very-well-behaved programs and restriction for $\pginline{Case}$ in Section~\ref{sect:pg}. To be a practical evlauation method, an extention of the target language is needed. After extention of the language, we can evaluate more various programs for experimental results.

@@

Third is introducing type systems to datatype of sources and view. If we introduce this, we can avoid runtime errors like statically-typed functional languages.For this, we need to investigate more about $construct\_dummy$, because the current definition that is used in our experiments %Section~\ref{sect:experiments}
will cause type errors.
